%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
{\color{awesome}\faFile*}\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Molecular Ecology 32, no. 5: 1034–1044. \textit{https://doi.org/10.1111/mec.16811}} % Journal
    {Expression of subunits of an insecticide target receptor varies across tissues, 
    life stages, castes, and species of social bees} % Title
    {Journal article} % Type
    {2023} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {Witwicka, A., \textbf{López-Osorio, F.}, Patterson, V., Wurm, Y.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Nature Communications 13, no. 1: 1180. \textit{https://doi.org/10.1038/s41467-022-28806-7}} % Journal
    {Recurring adaptive introgression of a supergene variant that determines social organization} % Title
    {Journal article} % Type
    {2022} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {Stolle, E., Pracana, R., \textbf{López-Osorio, F.}, Priebe, M., Hernández, G. L., \newline
        Castillo-Carrillo, C., Arias, M. C., Paris, C. V., Bollazzi, M., Priyam, A., Wurm, Y.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {in: Starr, C. K. (Ed.). Encyclopedia of Social Insects, pp. 365–368. \textit{https://doi.org/10.1007/978-3-030-28102-1\_42}} % Journal
    {Emery's rule} % Title
    {Book chapter} % Type
    {2021} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {López-Osorio, F.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Trends in Ecology \& Evolution 35, no. 5: 380–383. \textit{https://doi.org/10.1016/j.tree.2019.12.012}} % Journal
    {Healthy pollinators: Evaluating pesticides with molecular medicine approaches} % Title
    {Journal article} % Type
    {2020} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {\textbf{López-Osorio, F.} and Wurm, Y.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {The American Naturalist 189, no. 6: E138–151. \textit{https://doi.org/10.1086/691405}} % Journal
    {Convergent reversion to single mating in a wasp social parasite} % Title
    {Journal article} % Type
    {2017} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {Loope, K.J., \textbf{López-Osorio, F.}, Dvořák, L.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Molecular Phylogenetics and Evolution 107: 10–15. \textit{https://doi.org/10.1016/j.ympev.2016.10.006}} % Journal
    {Phylogenomic analysis of yellowjackets and hornets (Hymenoptera: Vespidae, Vespinae)} % Title
    {Journal article} % Type
    {2017} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {\textbf{López-Osorio, F.}, Pickett, K.M., Carpenter, J.M., Ballif, B.A., Agnarsson, I.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cladistics 32, no. 4: 406–425. \textit{https://doi.org/10.1111/cla.12138}} % Journal
    {Phylogeny, landmark analysis and the use of wing venation to study 
    the evolution of social wasps (Hymenoptera: Vespidae, Vespinae)} % Title
    {Journal article} % Type
    {2016} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {Perrard, A., \textbf{López-Osorio, F.}, Carpenter, J. M.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Royal Society Open Science 2, no. 9: 150159. \textit{https://doi.org/10.1098/rsos.150159}} % Journal
    {Phylogenetic tests reject Emery's rule in the evolution of social parasitism 
    in yellowjackets and hornets (Hymenoptera: Vespidae, Vespinae)} % Title
    {Journal article} % Type
    {2015} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {\textbf{López-Osorio, F.}, Perrard, A., Pickett, K. M., Carpenter, J. M., 
        Ballif, B. A., and Agnarsson, I.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Molecular Phylogenetics and Evolution 73: 190–201. \textit{https://doi.org/10.1016/j.ympev.2014.01.007}} % Journal
    {Phylogenetic relationships of yellowjackets inferred from nine loci 
    (Hymenoptera: Vespidae, Vespinae, \textit{Vespula} and \textit{Dolichovespula})} % Title
    {Journal article} % Type
    {2014} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {\textbf{López-Osorio, F.}, Pickett, K. M., Carpenter, J. M., Ballif, B. A., 
        and Agnarsson, I.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Conservation Biology 24, no. 5: 1359–1366. \textit{https://doi.org/10.1111/j.1523-1739.2010.01482.x}} % Journal
    {A phylogenetic approach to conserving Amazonian biodiversity} % Title
    {Journal article} % Type
    {2010} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {\textbf{López-Osorio, F.} and Miranda-Esquivel, D. R.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cladistics 24, no. 5: 813–824. \textit{https://doi.org/10.1111/j.1096-0031.2008.00203.x}} % Journal
    {What is PACT really?} % Title
    {Journal article} % Type
    {2008} % Date(s)
    {
      \begin{cvitems} % Author(s)
        \item {Arias, J. S., Garzón-Orduña, I. J., \textbf{López-Osorio, F.}, 
        Parada-Vargas, E. J., and Miranda-Esquivel, D. R.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
